---
title: "p8105_hw5_yw4251"
author: "You Wu"
date: 2023-11-12
output: github_document
---
# Problem 0
Load Necessary Packages.
```{r}
library(tidyverse)
library(purrr)
library(ggridges)
```

# Problem 2

Load and tidy the dataset.

```{r}
file_list = list.files(path = "data/",full.names = TRUE)
file_info_df = data.frame(file_name = file_list)

process_file = function(file_path) {
  parts = str_split(basename(file_path), "_|\\.")[[1]]
  arm = parts[1]
  subject_id = parts[2]

  data = read.csv(file_path) 

  data = mutate(data, subject_id = subject_id, arm = arm)

  return(data)
}

all_data = map_df(file_info_df$file_name, process_file)|>
  pivot_longer(
    week_1:week_8,
    names_to="week",
    values_to="outcome",
    names_prefix="week_"
  )|>
  mutate(
    week = as.numeric(week),
    arm=recode(arm, "con"="control", "exp"="experimental"),
    arm = as.factor(arm)           
  )

all_data
```

Make a spaghetti plot showing observations on each subject over time
```{r}
ggplot(all_data, aes(x = week, y = outcome, group = subject_id, color = subject_id)) +
  geom_line() +
  geom_point(size=1.5)+
  theme_minimal() +
  facet_grid(~arm)+
  labs(
    title = "Spaghetti Plot of Observations Over Time by Subjects",
    x = "Week",
    y = "Observation Outcome",
    color = "Subject ID"
  ) 
```

## _Differences between groups:_

**Trend**: The experimental group shows an increasing trend over time, suggesting a possible treatment effect, while the control group's trend is not consistently upward.

**Cohesion**: Outcomes vary significantly among subjects in both groups. The control group's outcomes are more closely bunched together, in contrast to the experimental group, where there's a broader spread of individual outcomes, suggesting a range of responses to the treatment.

**Time Change**: The distinction between the control and experimental groups grows more evident around the fourth or fifth week, suggesting this may be the period when the treatment begins to have a discernible impact.




# Problem 3

Generate 5000 datasets when `mu=0`.
```{r}
set.seed(1)
sim_mean_test <- function(mu,n=30, sigma = 5) {
  sim_data = tibble(
    x=rnorm(n=n, mean=mu, sd = sigma)
  )
  test_result = broom::tidy(t.test(sim_data$x))|>
    select(mu_hat=estimate, p.value)
  return(test_result)
}

sim_results_df_0 =   
  map(1:5000, \(i) sim_mean_test(0)) |> 
  bind_rows()

head(sim_results_df_0)

```

Repeat simulation for `mu={1,2,3,4,5,6}`.
```{r}
set.seed(1)
sim_results_df_1_6 = 
  expand_grid(
    mu = 1:6,
    iter = 1:50
  )|> 
  mutate(
    estimate_df = map(mu, sim_mean_test)
  ) |> 
  unnest(estimate_df)

power_analysis=sim_results_df_1_6|>
  group_by(mu)|>
  summarise(
    power=mean(p.value<0.05)
    avg_mu_hat = mean(mu_hat),
    avg_mu_hat_rejected = mean(mu_hat[p.value < 0.05])
    )

```



```{r}
power_analysis|>
  ggplot(aes(x=mu,y=power))+
  geom_point() +
  geom_line() +
  labs(title = "Power vs True Mean", x = "True Mean", y = "Power")
```

